SULI Report! (Working title)

### 2015-08-20 doc/suli-report-swe.tex
Cleaned up the SULI report appendix. #81

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{mathtools}
\usepackage{float}
\usepackage[format=plain]{caption}
\usepackage{subcaption}
%\usepackage{multicol}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

@@

\title{SULI Report!}
%\thanks{A footnote to the article title}%

@@

Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see appendix A. Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see appendix B.

@@

@@

The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}. The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes. The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations. Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute. However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute. Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales. On average, the shear power is underpredicted by 117\%.
%% Ellipticity-Ellipticity Correlation
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.475\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes. While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute. The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation. The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales. The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
        \label{gg_corr}
    \end{subfigure}
    ~~
    \begin{subfigure}{0.475\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arcminute to $R=8$ arcminutes, all plotted in purple with various line styles. These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
        \label{gg_corr_series}
    \end{subfigure}
    \caption{}
\end{figure}

@@

I would like to thank the Department of Energy for funding this research and giving me the opportunity to conduct research on (cutting edge physics). This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC). Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.

This work was supported in part by the U.S. Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).

@@

@@

%\end{document}

\subsection{Visualizing Correlation Functions}

At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize. While by no means a thorough or mathematical analysis (see (cite) for a general introduction to correlation functions, and (cite) for their many applications in cosmology), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and place the main results of this paper in more context.

%% Correlation Colormaps
\begin{figure*}
    \centering
    \begin{subfigure}[H]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/xip_colormap.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap. The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
        \label{xip_colormap}
    \end{subfigure}
    ~
    \begin{subfigure}[H]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/xix_colormap.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap. While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
        \label{xix_colormap}
    \end{subfigure}
    \caption{Correlation pair colormaps for $\xi_+$ and $\xi_\times$.}
    \label{corr_colormaps}
\end{figure*}

%% Color-Coded Correlation Un-lensed
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{A set of background sources around a foreground lens (blue dot). The size and orientation of each stick represents the intrinsic source ellipticity and is colored by the distance away from the lens.}
        \label{color_corr_unlensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme. Otherwise, the correlation is not plotted.}
        \label{corr_dist_unlensed}
    \end{subfigure}
    \caption{Correlation visualization for un-lensed galaxies.}
    \label{colored_corr}
\end{figure}

%% Color-Coded Correlation Lensed
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass. Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
        \label{color_corr_lensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme. Otherwise, the correlation is not plotted.}
        \label{corr_dist_lensed}
    \end{subfigure}
    \caption{Correlation visualization for lensed galaxies.}
    \label{colored_corr_lensed}
\end{figure}

@@

\subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}

\begin{itemize}
\item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
\item Here we derive the connection between the two
\item Definitions of each, along with references
\end{itemize}

From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
\begin{align}
\xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
\xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
\end{align}

where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\

From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
\begin{align}
\xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
\xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
\end{align}

where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\

\section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}

Starting with Schneider's definition, observe that
\begin{align*}
\xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
&=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
&=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
\end{align*}

Using the trig identities
\begin{align}
\cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
\sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
\end{align}

and the linearity of the expectation operator, it is straightforward to show that
%\begin{align*}
%\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
%&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
%\end{align*}
$$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$

Now using the identity
\begin{equation}\label{trig2}
\cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
\end{equation}

the previous equation can be written as

\begin{align*}
\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
&=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
\end{align*}

Using the complex number identities

\begin{align}
\operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
\operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
\end{align}

it follows that

\begin{align*}
\xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
&=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
&=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
\end{align*}

\section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}

The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
\begin{align*}
\xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
\end{align*}

Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes

\begin{align*}
\xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
&=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
\end{align*}

Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
\begin{align*}
\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
\end{align*}

Now observe that for two complex numbers $a$ and $b$, it is true that

$$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$

Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that

$$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$

Combining this with our previous result, this means that

$$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$

\section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}

Starting from Schneider's definition of $\xi_\times$,

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{mathtools}
%\usepackage{float}
\usepackage[format=plain]{caption}
\usepackage{subcaption}
%\usepackage{multicol}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\raggedbottom

@@

\title{SULI Report! (Working title)}
%\thanks{A footnote to the article title}%

@@

Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. The ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. For readers that are unfamiliar with correlation functions in the context of cosmology or want a visual aid, see the appendix. Both correlation functions are used in this work to measure how well the \texttt{Pangloss} framework models weak lensing by dark matter structures using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition and the more common Schneider definition \cite{schneider}, see (???).

@@

%% Ellipticity-Ellipticity Correlation
\begin{figure}
    \centering
    \begin{subfigure}{0.475\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/gg_corr.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The ellipticity-ellipticity correlation function for 3,240 sources at separation distances from 0.1 arcminutes to 2 arcminutes and a lightcone radius of $R=2$ arcminutes. While the correlation of the intrinsic ellipticities before lensing (blue) shows no correlation, the correlation of the ray-traced ellipticities (green) and halo model predicted ellipticities (purple) both show significant positive correlation on scales up to 1 arcminute. The halo model predicts a small negative correlation above this scale, while the ray-tracing shows positive correlation on all scales.}
        %The correlation of the intrinsic ellipticities before lensing is plotted in blue, and shows no correlation. The correlation of the true ray-traced ellipticities is plotted in green and shows significant positive correlation on all scales. The halo predicted correlation, plotted in purple, shows significant positive correlation until a separation distance of 0.8 arcminutes.
        \label{gg_corr}
    \end{subfigure}
    ~~
    \begin{subfigure}{0.475\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/gg_corr_series.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The ellipticity-ellipticity correlation functions for a series of halo model frameworks with increasing lightcone radii from $R=1$ arcminute to $R=8$ arcminutes, all plotted in purple with various line styles. These are compared to the same ray-traced correlation from Figure \ref{gg_corr}.}
        \label{gg_corr_series}
    \end{subfigure}
    \caption{}
\end{figure}

@@

The first test of the halo model was with the ellipticity-ellipticity correlation function with a lightcone radius of 2 arcminutes which is given in Figure \ref{gg_corr}. The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes. The correlation function of the intrinsic ellipticities plotted in blue shows no significant deviation from zero as expected, as before lensing the galaxies had random orientations. Both the ray-traced, plotted in green, and halo model, plotted in purple, ellipticities show positive correlation on small scales up to a separation of 1 arcminute. However, the ray-traced correlation is positive on all calculated scales while the halo model does not predict any significant correlation at separations above 1 arcminute. Additionally, while the shapes of the correlation functions for both sets of lensed ellipticities agree well until 1 arcminute, there is a clear systematic underprediction of shear power by the halo model on all scales. On average, the shear power is underpredicted by 117\%.

@@

I would like to thank the Department of Energy for funding this research and giving me this wonderful opportunity, as well as SLAC National Laboratory for hosting me. This work was greatly aided by numerous conversations with Risa Wechsler from Stanford University and Matt Becker from the Kavli Institute for Particle Astrophysics and Cosmology (KIPAC). Finally, I am incredibly grateful to Phil Marshall for his unending support, patience, and guidance throughout this research.
This work was supported in part by the U.S. Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).

@@

\subsection*{Visualizing Correlation Functions}

%% Correlation Colormaps
\begin{figure}[!b]
    \centering
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/xip_colormap.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The positive tangential component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap. The correlation component is positive for parallel galaxies, negative for perpendicular galaxies, and zero for galaxies offset by 45$^\circ$.}
        \label{xip_colormap}
    \end{subfigure}
    ~
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/xix_colormap.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The cross component of the $\varepsilon-\varepsilon$ correlation as a function of galaxy orientation plotted as a colormap. While the pattern is more complicated than that of the tangential component, note that the correlation value is zero for all preferred orientations after lensing.}
        \label{xix_colormap}
    \end{subfigure}
    \caption{Correlation pair colormaps for $\xi_+$ and $\xi_\times$.}
    \label{corr_colormaps}
\end{figure}

At first encounter, the use of correlation functions to analyze data can be difficult to comprehend, let alone visualize. While by no means a thorough or mathematical analysis (see \cite{correlation_functions} for a more formal introduction), I have created some explanatory plots to aid in visualizing how weakly lensed ellipticities can be measured with correlation functions and place the main results of this paper in more context.

%% Color-Coded Correlation Un-lensed
\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{A set of background sources around a foreground lens (blue dot). The size and orientation of each stick represents the intrinsic source ellipticity and is colored by the distance away from the lens.}
        \label{color_corr_unlensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme. Otherwise, the correlation is not plotted.}
        \label{corr_dist_unlensed}
    \end{subfigure}
    \caption{Correlation visualization for un-lensed galaxies.}
    \label{colored_corr}
\end{figure}

%% Color-Coded Correlation Lensed
\begin{figure}
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass. Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
        \label{color_corr_lensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme. Otherwise, the correlation is not plotted.}
        \label{corr_dist_lensed}
    \end{subfigure}
    \caption{Correlation visualization for lensed galaxies.}
    \label{colored_corr_lensed}
\end{figure}

@@

@@

% \subsection{Deriving the Standard Correlation Function Definition from \texttt{TreeCorr}'s Definition}

% \begin{itemize}
% \item Introduction to difference between the common Schneider definition of lensing correlation functions and that used by Jarvis`s \texttt{TreeCorr} code
% \item Here we derive the connection between the two
% \item Definitions of each, along with references
% \end{itemize}

% From Jarvis \href{http://arxiv.org/pdf/astro-ph/0307393v2.pdf}{(Page 3)}:
% \begin{align}
% \xi_+&=\left<\gamma_i\gamma_j^*\right>=\texttt{xip}+i(\texttt{xip\_im})\label{s+}\\
% \xi_-&=\left<\gamma_i\gamma_je^{-4i\alpha}\right>=\texttt{xim}+i(\texttt{xim\_im})\label{s-}
% \end{align}

% where $\alpha$ is the angle between the two objects $i,j$ and each $\gamma$ is given by $\gamma_n=|\gamma_n|e^{2i\theta_n}$ in polar form.\\

% From Schneider \href{http://arxiv.org/pdf/astro-ph/0509252v1.pdf}{(Page 92)}:
% \begin{align}
% \xi_\pm&=\left<\gamma_{i_t}\gamma_{j_t}\right>\pm\left<\gamma_{i_\times}\gamma_{j_\times}\right>\label{s+-}\\
% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\label{sx}
% \end{align}

% where $\gamma_{n_t}=-\operatorname{Re}\left(\gamma_n e^{-2i\alpha}\right)$ and $\gamma_{n_\times}=-\operatorname{Im}\left(\gamma_n e^{-2i\alpha}\right)$.\\

% \section*{Schneider's $\xi_+$ to Jarvis's \texttt{xip}}

% Starting with Schneider's definition, observe that
% \begin{align*}
% \xi_+&=\left<\gamma_{i_t}\gamma_{j_t}\right>+\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
% &=\left<\operatorname{Re}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Re}\left(\gamma_je^{-2i\alpha}\right)\right>+\left<\operatorname{Im}\left(\gamma_ie^{-2i\alpha}\right)\cdot\operatorname{Im}\left(\gamma_je^{-2i\alpha}\right)\right>\\
% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Re}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>+\left<\operatorname{Im}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>+\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>.
% \end{align*}

% Using the trig identities
% \begin{align}
% \cos(u)\cos(v)&=\frac{1}{2}\left[\cos(u-v)+\cos(u+v)\right],\\
% \sin(u)\sin(v)&=\frac{1}{2}\left[\cos(u-v)-\cos(u+v)\right],
% \end{align}

% and the linearity of the expectation operator, it is straightforward to show that
% %\begin{align*}
% %\xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\right>\cdot\left(\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)+\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>+\left<\frac{1}{2}\left[\cos\left(2(\theta_i-\theta_j)\right)-\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right]\right>\right)\\
% %&=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.
% %\end{align*}
% $$\xi_+=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\theta_j)\right)\right>.$$

% Now using the identity
% \begin{equation}\label{trig2}
% \cos(u\pm v)=\cos\left(u\right)\cos\left(v\right)\mp\sin\left(u\right)\sin\left(v\right),
% \end{equation}

% the previous equation can be written as

% \begin{align*}
% \xi_+&=\left<|\gamma_i|\cdot|\gamma_j|\cdot\left[\cos\left(2\theta_i\right)\cos\left(2\theta_j\right)+\sin\left(2\theta_i\right)\sin\left(2\theta_j\right)\right]\right>\\
% &=\left<\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\right>.
% \end{align*}

% Using the complex number identities

% \begin{align}
% \operatorname{Re}(z)&=\frac{1}{2}\left[z+z^*\right],\label{complex1}\\
% \operatorname{Im}(z)&=\frac{1}{2i}\left[z-z^*\right]\label{complex2},
% \end{align}

% it follows that

% \begin{align*}
% \xi_+&=\left<\frac{1}{4}\left[(\gamma_i+\gamma_i^*)(\gamma_j+\gamma_j^*)-(\gamma_i-\gamma_i^*)(\gamma_j-\gamma_j^*)\right]\right>\\
% &=\left<\frac{1}{2}\left[\gamma_i\gamma_j^*+(\gamma_i\gamma_j^*)^*\right]\right>\\
% &=\left<\operatorname{Re}(\gamma_i\gamma_j^*)\right>=\texttt{xip}.
% \end{align*}

% \section*{Schneider's $\xi_-$ to Jarvis's \texttt{xim}}

% The first few steps are identical to the previous section besides the negative in the definition of $\xi_-$, giving
% \begin{align*}
% \xi_-&=\left<\gamma_{i_t}\gamma_{j_t}\right>-\left<\gamma_{i_\times}\gamma_{j_\times}\right>\\
% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\cos\left(2(\theta_j-\alpha)\right)\right>-\left<|\gamma_i|\cdot|\gamma_j|\sin\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\right>\\
% &=\left<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i+\theta_j-2\alpha)\right)\right>.
% \end{align*}

% Now using Equation \eqref{trig2} twice, first letting $u=2(\theta_i+\theta_j)$ and $v=-4\alpha$, and then letting $u=2\theta_i$ and $v=2\theta_j$, this equation becomes

% \begin{align*}
% \xi_-&=\left<|\gamma_i|\cdot|\gamma_j|\Big(\left[\cos(2\theta_i)\cos(2\theta_j)-\sin(2\theta_i)\sin(2\theta_j)\right]\cos(4\alpha)+\left[\sin(2\theta_i)\cos(2\theta_j)+\cos(2\theta_i)\sin(2\theta_j)\right]\sin(4\alpha)\Big)\right>\\
% &=\Big<\big[\operatorname{Re}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)-\operatorname{Im}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\cos(4\alpha)+\big[\operatorname{Im}(\gamma_i)\cdot\operatorname{Re}(\gamma_j)+\operatorname{Re}(\gamma_i)\cdot\operatorname{Im}(\gamma_j)\big]\sin(4\alpha)\Big>.
% \end{align*}

% Using the identities \eqref{complex1} and \eqref{complex2}, and simplifying the leftover terms, this equation can be shown to equal
% \begin{align*}
% \xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>.
% \end{align*}

% Now observe that for two complex numbers $a$ and $b$, it is true that

% $$\operatorname{Re}(a\cdot b^*)=\operatorname{Re}(a)\cdot\operatorname{Re}(b)+\operatorname{Im}(a)\cdot\operatorname{Im}(b).$$

% Then setting $a=\gamma_i\gamma_j$ and $b=e^{4i\alpha}$, it must be true that

% $$\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)=\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha).$$

% Combining this with our previous result, this means that

% $$\xi_-=\big<\operatorname{Re}(\gamma_i\gamma_j)\cos(4\alpha)+\operatorname{Im}(\gamma_i\gamma_j)\sin(4\alpha)\big>=\left<\operatorname{Re}\left(\gamma_i\gamma_je^{-4i\alpha}\right)\right>=\texttt{xim}.$$

% \section*{Schneider's $\xi_\times$ to Jarvis's $\frac{1}{2}\left(\texttt{xim\_im}-\texttt{xip\_im}\right)$}

% Starting from Schneider's definition of $\xi_\times$,

% \begin{align*}
% \xi_\times&=\left<\gamma_{i_t}\gamma_{j_\times}\right>\\
% &=\left<\operatorname{Re}\left(|\gamma_i|e^{2i(\theta_i-\alpha)}\right)\cdot\operatorname{Im}\left(|\gamma_j|e^{2i(\theta_j-\alpha)}\right)\right>\\
% &=\big<|\gamma_i|\cdot|\gamma_j|\cos\left(2(\theta_i-\alpha)\right)\sin\left(2(\theta_j-\alpha)\right)\big>.\\
% \end{align*}
